\Large\bf Simultaneous Elicitation of Committee and Voters Preferences

### 2019-04-01 RJCIA2019/short_draft.tex
more corrections

\section{Introduction}
%Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc) whose final goal is to find a consensus choice.
%In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
In a traditional social choice setting, both the social function and the full preference orderings of the agents are expressed beforehand. Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences. 
Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information. We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.

\section{Partial information}
\label{sec:background}
We assume defined a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents. Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
A {\em profile} is the association of a preference to each agent and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by $\profile=(v_1,\ldots,v_n) \in V$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
%Given $V$ the set of possible preference profiles, a social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners; where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e. 
%${\ppref_j} \subseteq {\pref_j^*}$.
$a \ppref_j b ⇒ a \pref_j^* b$.
%\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
%We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference. A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
%We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.

>>>>

\section{Introduction}
%Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc) whose final goal is to find a consensus choice.
%In this contexts, a natural approach consists in looking at methods from social choice and see how they can be adapted for group decision-making in a computerized setting.
In a traditional social choice setting, both the social choice function and the full preference orderings of the agents are expressed beforehand. Nevertheless, requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost), especially for decisions with large sets of alternatives.
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015} of agents’ preferences. 
Furthermore, several situations for which it may not be easy to precisely define the voting rule exist.
Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
The work of Cailloux and Endriss \citep{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
In this paper we consider that both the agents’ preferences and the social choice rule are partially specified.
We develop methods for computing the minimax-optimal alternative using positional scoring rules and we provide incremental elicitation methods to acquire relevant preference information. We then discuss several heuristics that determine queries, either to an agent or to the committee, that quickly reduce minimax regret.
While previous works have considered either partial information about the agents preferences or a partially specified aggregation method, we do not know of any work considering both sources of uncertainty at the same time.

\section{Partial information}
\label{sec:background}
We consider a set $A$ of $m$ alternatives (products, restaurants, public projects, etc.) and a set $\set{1, …, n}$ of agents. Each agent $j$ comes from an infinite set $\N$ of potential agents and is associated to her “real” preference order $\pref_j \in \linors$ which is a linear order (connected, transitive, asymmetric relation) over the alternatives.
A {\em profile} is the association of a preference to each agent and it is equivalently represented by $(\pref_1,\ldots,\pref_n)$ or by $\profile=(v_1,\ldots,v_n) \in V$ where $v_j(i) \in \set{1, \ldots, m}$ denotes the rank (position) of alternative $i$ in the preference order $\pref_j$.
%Given $V$ the set of possible preference profiles, a social choice function $f : V \rightarrow \powersetz{A}$ associates a profile with a set of winners; where $\powersetz{A}$ represents the set of subsets of $A$ except for the emptyset.
A social choice function associates a profile with a set of winners; we consider {\em positional scoring rules (PSR)}, which attach weights to positions according to the scoring vector $(w_1, \ldots, w_m)$.
An alternative obtains a score that depends on the rank obtained in each of the preference orders and the winners are the alternatives with highest scores.
In this work we assume fixed, but unknown, a profile $\profile^* = (\pref^*_j, j \in \{1, \ldots, n\})$ and a weight vector $\w^*$.
Our knowledge at a given time of the preference of agent $j$ is encoded by a partial order over the alternatives, thus a transitive and asymmetric binary relation, denoted by $\ppref_j$; we assume that preference information is truthful, i.e. 
%${\ppref_j} \subseteq {\pref_j^*}$.
$a \ppref_j b ⇒ a \pref_j^* b$.
%\commentOC{Or simply ${\ppref_j} \subseteq {\pref_j^*}$, if you need to save space}
%We use $\pinc$ to denote incomparability, that is $a \pinc_{j} b$ iff $a \nppref_j b \wedge b \nppref_j a$.
An incomplete profile $\pprofile = (\ppref_1, \ldots, \ppref_n)$ maps each agent to a partial preference. A completion of $\ppref_j$ is any linear order $\pref$ that extends $\ppref_j$ and we indicate with $C(\ppref_j) = \set{{\succ} \in \linors \suchthat {\ppref_j} \subseteq {\succ}}$ the set of possible completions of $\ppref_i$.
%We let $C(\pprofile)=C(\ppref_1)\times … \times C(\ppref_n)$ be the set of complete profiles extending $p$. Note that $\profile^* \in C(\pprofile)$.
